Supplemental Materials for the paper: \\ Pesticide exposure in small streams in Germany

### 2016-09-27 article.tex
title
meta analysis of single compound models.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[Pesticides small streams]{Pesticide exposure in small streams in Germany}
% \abbreviations{mo, neon, ra, tu, fw}
\keywords{Monitoring, Neonicotinoid, Risk Assessment Toxic Units, Freshwater}
% RAC,

@@

\begin{align}
RQ_i \sim ZAGA(\mu_i, \pi_i) = 
  \begin{cases}
    (1 - \pi_i)   & \quad  \text{if } y < LOQ \\
    \pi_i \times f_{Gamma} (\mu_i) & \quad \text{if } y \ge LOQ \\
  \end{cases}
  \label{eqn:eqn3}
\end{align}

$\pi_i$ denotes the probability of a observation i being above LOQ and $f_{Gamma}$ denotes the gamma function and is used for values greater LOQ, where $\mu$ is the mean of the gamma function.
We used the log(x+0.05) transformed precipitation at sampling date ($log~prec_0$) and the day before ($log~prec_{-1}$), as well as quarters of the year ($season_{Q1-Q4}$) as linear predictors for $\mu$ and $\pi$.
To account for temporal autocorrelation and differences between federal $state$ we used the $site$ nested within $state$ as random intercepts.

\begin{align}
\begin{split}
\log(\mu_{ijk}) = log~prec_{0 ijk} + log~prec_{-1 ijk} + season_{ijk} + state_j + site_{jk}\\
logit(\pi_{ijk}) = log~prec_{0 ijk} + log~prec_{-1 ijk} + season_{ijk} + state_j + site_{jk}\\
state_{j} \sim N(0, \sigma^2_{state}) \\
site_{jk} \sim N(0, \sigma^2_{site})
\end{split}
\label{eqn:eqn4}
\end{align}

Changes in $\mu$ can be interpreted as changes in the absolute value of RQ, whereas changes in $\pi$ can be interpreted as changes in the probability that there is any risk.
We fitted this model separately to each compound with a RAC, with at least 1000 samples and more then 5\% of values above quantification limit (see Supplement, Table S3 for a list of compounds). 
We implemented the model using the gamlss package \cite{stasinopoulos_generalized_2007}.

@@

\subsection{Effect of precipitation on pesticide exposure}
The spatio-temporal intersection revealed that 5\% of the samples were taken at or after days with rainfall events greater than 10mm / day (Supplement, Figure S6).
Precipitation at the day before ($log~precip_{-1}$) sampling increased $\mu$ and also $\pi$ for nearly all analysed compounds. 
The effects were less pronounced ($\pi$) or not clearly directed ($\mu$) for precipitation at the day of sampling ($log~precip_{0}$)(Figure \ref{fig:fig5}, top).

Q2, Q3 and Q4 showed generally higher $\mu$ than in Q1, with smallest differences for Q4.
An exception was the herbicide Diflufenican, that showed througout all quarters lower RQ in Q2-Q4 compared to Q1 (Figure \ref{fig:fig5}, bottom and Supplement Table S4).
We found similar effects of season on $\pi$, but with more compounds showing a reduction in $\pi$.

\begin{figure}[h]
  \includegraphics[width=0.95\textwidth]{figure5.pdf}
  \caption{Estimated coefficients and their 95\% CI for the model described in equations \ref{eqn:eqn3} and \ref{eqn:eqn4} for each of the 24 analysed compounds (see Supplement Tables S3 and S4 for a list of compounds from top to bottom and their respective coefficients). Left column: Effect on mean RQ ($\mu$); Right column: effect on the probability that RQ \textgreater 0 ($\pi$).
  Coefficients where the CI encompasses zero are shown in gray colour.
  }
  \label{fig:fig5}
\end{figure}

@@

\begin{figure}[h]
  \includegraphics[width=0.6\textwidth]{figure6.pdf}
  \caption{15 compounds with highest risk quotients in SWB. Non-detects are not shown due to the logarithmic axis. Numbers on the right give the percentage of RQ \textgreater 0 and total number of samples.
  }
  \label{fig:fig6}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[Pesticides small streams]{Pesticides in small streams in Germany}
% \abbreviations{mo, neon, ra, tu, fw}
\keywords{Monitoring, Neonicotinoid, Risk Assessment Toxic Units, Freshwater}
% RAC,

@@

\begin{align}
RQ_i \sim ZAGA(\mu_i, \sigma, \nu_i) = 
  \begin{cases}
    (1 - \nu_i)   & \quad  \text{if } y < LOQ \\
    \nu_i \times f_{Gamma} (\mu_i, \sigma) & \quad \text{if } y \ge LOQ \\
  \end{cases}
  \label{eqn:eqn3}
\end{align}

$\nu_i$ denotes the probability of a observation i being above LOQ and $f_{Gamma}$ denotes the gamma function and is used for values greater LOQ, with $\mu$ being the mean and $\sigma$ the standard deviation.
We used the $log(x+0.05)$ transformed precipitation at sampling date ($log~prec_0$) and the day before ($log~prec_{-1}$), as well as quarters of the year ($season_{Q1-Q4}$) as linear predictors for $\mu$ and $\nu$. 
$\sigma$ was assumed to be constant. 
To account for temporal autocorrelation and differences between federal states we used $site$ nested within $state$ as random intercepts:

\begin{align}
\begin{split}
\log(\mu_{ijk}) = log~prec_{0 ijk} + log~prec_{-1 ijk} + season_{ijk} + state_j + site_{jk}\\
logit(\nu_{ijk}) = log~prec_{0 ijk} + log~prec_{-1 ijk} + season_{ijk} + state_j + site_{jk}\\
state_{j} \sim N(0, \sigma^2_{state}) \\
site_{jk} \sim N(0, \sigma^2_{site})
\end{split}
\label{eqn:eqn4}
\end{align}

Changes in $\mu$ can be interpreted as changes in the absolute value of RQ, whereas changes in $\nu$ can be interpreted as changes in the probability of exceeding LOQ.
We fitted this model separately to each compound with a RAC, at least 1000 samples and more then 5\% of values above quantification limit (see Supplement, Table S3 for a list of compounds). 
We implemented the model using the gamlss package \cite{stasinopoulos_generalized_2007}.

@@

\subsection{Effect of precipitation on pesticide exposure}
The spatio-temporal intersection revealed that 5\% of the samples were taken at or after days with rainfall events greater than 10mm / day (Supplement, Figure S6).
Precipitation at the day before ($log~precip_{-1}$) sampling increased $\mu$ and also $\nu$ for nearly all analysed compounds. 
The effects were less pronounced ($\nu$) or not clearly directed ($\mu$) for precipitation at the day of sampling ($log~precip_{0}$)(Figure \ref{fig:fig5}, top).

Q2, Q3 and Q4 showed generally higher $\mu$ than in Q1, with smallest differences for Q4.
An exception was the herbicide Diflufenican, that showed througout all quarters lower RQ in Q2-Q4 compared to Q1 (Figure \ref{fig:fig5}, bottom and Supplement Table S4).
We found similar effects of season on $\nu$, but with more compounds showing a reduction in $\nu$.

\begin{figure}[ht]
  \includegraphics[width=0.95\textwidth]{figure5.pdf}
  \caption{Estimated coefficients and their 95\% CI for the model described in equations \ref{eqn:eqn3} and \ref{eqn:eqn4} for each of the 24 analysed compounds (see Supplement Tables S3 and S4 for a list of compounds from top to bottom and their respective coefficients). Left column: Effect on mean RQ ($\mu$); Right column: effect on the probability that RQ \textgreater 0 ($\nu$).
  Coefficients where the CI encompasses zero are shown in gray colour.
  }
  \label{fig:fig5}
\end{figure}

\todo{rewrite + new figures to supplement}

@@

\begin{figure}[ht]
  \includegraphics[width=0.6\textwidth]{figure6.pdf}
  \caption{15 compounds with highest risk quotients in SWB. Non-detects are not shown due to the logarithmic axis. Numbers on the right give the percentage of RQ \textgreater 0 and total number of samples.
  }
  \label{fig:fig6}
\end{figure}

### 2016-09-27 supplement/Supplemental_Materials.tex
meta analysis of single compound models.

>>>>

\begin{figure}[h]
	\centering
	\includegraphics[width = 0.8\textwidth]{coefs}
	\caption[Graphical representation of coefficients from table \ref{tab:var_model_coef}.]{Graphical representation of coefficients from table \ref{tab:var_model_coef}. Top row: Effect of precipitation at day before sampling and at day of sampling. Bottom row: estimates for the four Quarters. Each dot represent one compound. Coefficients where the CI encompasses zero are shown in gray colour. Coefficients are shown on the link scale (log for $\mu$ and logit for $\nu$).}
	\label{fig:coefs}
\end{figure}
